Template for indicator documentation

### 2023-03-14 climate_indicators_explained.Rmd
add chapter medain-summer-temp and rename generic chapter
include chapter in yml

# Climate indicators

@@

This chapters describes the development of a workflow for generating or preparing indicators based on interpolated climate data from [SeNorge](https://senorge.no/).

>>>>

# Climate indicators explained {#climate-indicators-explained}

@@

This chapters describes the development of a workflow for generating or preparing indicators based on interpolated climate data from [SeNorge](https://senorge.no/). I describe the process using dummy data and also discuss alternate approaches and dead ends that occured in the development process. For a succinct workflow example for a spesific indikcator, see [Median summer temperature](#median-summer-temp).
